\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
more comments

\textbf{Reasoning Requires Non-Overridable.} This compilation strategy
can allow fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, there are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

@@

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable field is still not expressive enough to achieve the full extent of the dependent type programming. There are cases reasoning and overriding are both required, especially when we need to use Coq to do computation. For example, we may want a field to be an arbitrary monotonic function. Again, we cannot split into two fields \mintinline{Coq}{(f : nat → nat; p : monotonic f)} because to provide "p" we need to have concrete definition of "f" in the family type, which makes "f" non-overridable at all. One option is to use sigma type \mintinline{Coq}{{f | monotonic f}} but that is cumbersome when we have a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---basically we allow the users to specify the family/compiled module type, and thus we can have a \textit{locally transparent}, \textit{non-overridable} field located in a \textit{overridable} family. Using the above example, we simply make \mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an \textit{overridable} family, but "f" to be non-overridable and transparent on its definition, and thus we can prove "p". Once we want to swap the implementation, we just override the whole ``sealed'' family.

This ``sealed'' family actually simulate interface to a certain level---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

>>>>

\textbf{Reasoning Requires Non-Overridable.}\YZ{At this point in this section, overriding has not been discussed yet, but it is already discussing non-overridables. Should probably discuss the extensibility first.}
This compilation strategy
can allow fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, there are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

@@

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{(f : nat → nat; p : monotonic f)}\YZ{Is this semicolon syntax valid Coq syntax?} because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the family/compiled module type\YZ{I don't understand "specify the family/compiled module type"}, and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply make
\mintinline{Coq}{(f : nat → nat, p : monotonic f)} together inside an
\textit{overridable} family, but "f" to be non-overridable and
transparent on its definition, and thus we can prove "p". Once we want
to swap the implementation of "f", we just override the whole ``sealed''
family.

``Sealed'' families actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property
